Investigation on GIT

### 2010-04-25 paper.tex
add branch, tag and merge

Operations being done offline also means that there is no network latency to be worried of,
and can be more performant. Performance is important in VCS because if the revision
system is too slow, it might affect the workflow of the tool. Operations like commits, 
searching through the history, taking the diff out of two branches,  
% Explicaremos el principio de funcionamiento de la herramienta distribuida 
% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
% su propio repositorio, que las versiones pueden ser infinitas (por más que 
% haya una(s) maestra(s)), que se puede trabajar offline, etc.

@@

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well tested and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done, and could ``break the build''. 
In a DVCS the nature of the commits change, since commits are made in the local 
repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.

%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

\subsection{Branching and Merging}

@@

@@

Estos dos conceptos son distintos al check in / check out centralizado, 
consisten en el envío o recepción de commits entre dos repositorios. Aquí 
explicaremos un poco en que consisten y cuando hay que usar uno u otro.

>>>>

% Explicaremos el principio de funcionamiento de la herramienta distribuida 
% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
% su propio repositorio, que las versiones pueden ser infinitas (por más que 
% haya una(s) maestra(s)), que se puede trabajar offline, etc.

@@

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

\subsection{Tagging and Branching}

@@

Centralized VCS's like Subversion makes certain copies through history called tags. But on Git we have more tools, one of them is that we can have an arbitrary description attached in the tag, in fact, you can store the whole release announcements here. Moreover, as with the commit, is stored the identity of who made the tag and this identity can be verified if we add a cryptographically PGP sign to the tag

\subsection{Merging}

Merge on Git between branches is great!, all the history of both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches, they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any conflict and let you resolve them.

@@

When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
Push refers to taking all my changes and add them to the repository of another co-worker. But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.

%Estos dos conceptos son distintos al check in / check out centralizado, 
%consisten en el envío o recepción de commits entre dos repositorios. Aquí 
%explicaremos un poco en que consisten y cuando hay que usar uno u otro.
